\vspace{-2.25cm} Development of Ocular Disease Auxiliary Diagnosis System

### 2024-08-12 Paper/Paper.tex
Add paper framework to tex doc

>>>>

	\section{Model Overview}

		Fig: OCT abnormities
		Fig: Fundus abnormities
		Fig: From Abnormity to Disease
		Fig: 3 parts
		Fig: fusion

	\section{Methodology}

		\subsection{Abnormity Models}

			\subsubsection{Data Preparation}

				Table: Data source
				CycleGAN
					Fig: Intro
					Table: selection rates
					selection criteria
				Transformations

			\subsubsection{Training}

				intro to five-fold train/valid
				parameters used
				Fig: how batchSize, LR, and featureLayerSize affects accuracy

			\subsubsection{Testing}

				numerical results calculation method
				t-SNE intro
				GradCAM intro

		\subsection{Diagnosis Model}

			\subsubsection{Data Preparation}

				fusion method
				how to choose data (with an example)

			\subsubsection{Training}

				parameters used
				Fig: how batchSize, LR, gradeSize affects accuracy

			\subsubsection{Testing}

				numerical results list
				t-SNE

	\section{Results and Discussion}

		\subsection{Abnormity Models}

			For both OCT and Fundus:
				Fig: accuracy and loss over epochs
				Table: total accuracy and abnormities accuracies
				Table: numerical results for each abnormity
				Fig: ROC for each abnormity
				Fig: GradCAM example

		\subsection{Diagnosis Model}

			Fig: accuracy and loss over epochs
			Table: total accuracy and abnormities accuracies
			Table: numerical results for each disease
			Fig: ROC for each disease

	\section{Appendix}

		Google Image source links
		Table: OCT abnormities description
		Table: Fundus abnormities description
